Draft

### 2020-07-28 Draft.Rmd
CAD6.3

Supp_Tab <- read_csv("Results/Supp Tab.csv")
Supp_Tab$Score[Supp_Tab$DeepLearningSystem %in% "CAD4TB"] <- Supp_Tab$Score[Supp_Tab$DeepLearningSystem %in% "CAD4TB"]/100
Supp_Tab <- subset(Supp_Tab, Supp_Tab$Site %in% "BGD")
# View(Supp_Tab)
Supp_Tab <- Supp_Tab[Supp_Tab$Score %in% c(0.6, 0.7, 0.8), c(2:4, 8, 9)]
knitr::kable(Supp_Tab)
```

>>>>

Supp_Tab <- read_csv("Results/Supp Tab.csv")
Supp_Tab_4digits <- read_csv("Results/Supp Tab 4digits.csv")
Supp_Tab$Score[Supp_Tab$DeepLearningSystem %in% "CAD4TB"] <- Supp_Tab$Score[Supp_Tab$DeepLearningSystem %in% "CAD4TB"]/100
Supp_Tab <- subset(Supp_Tab, Supp_Tab$Site %in% "BGD")
# View(Supp_Tab)
# Supp_Tab <- Supp_Tab[Supp_Tab$Score %in% c(0.6, 0.7, 0.8), c(2:4, 8, 9)]
knitr::kable(Supp_Tab)
```

### 2020-07-28 ROCs.Rmd
CAD6.3

### Histogram 
```{r Histogram, fig.width=8, fig.height=5,}
# make it long
Adult_Valid$qXRv2_100 <- Adult_Valid$qXRv2*100

Adult_Valid_long <- gather(Adult_Valid, DeepLearningSystem, AbnormalityScore, CAD4TB6, qXRv2_100)

# p <- ggplot(Adult_Valid,aes(CAD4TB6))
# p <- ggplot(Adult_Valid,aes(qXRv2))
# p <- ggplot(Adult_Valid,aes(DrCADxScore))

@@

# library(moments)
# skewness(Adult_Valid[Adult_Valid$Xpert2Outcome_num ==1, 28]) #28 CAD4TB6, 29 qXRv2, 33 Lunit
# skewness(Adult_Valid[Adult_Valid$Xpert2Outcome_num ==1, 29]) #29 qXRv2, 33 Lunit
# skewness(Adult_Valid[Adult_Valid$Xpert2Outcome_num ==1, 33]) #33 Lunit
# 
# skewness(Adult_Valid[Adult_Valid$Xpert2Outcome_num ==0, 28]) #28 CAD4TB6, 29 qXRv2, 33 Lunit
# skewness(Adult_Valid[Adult_Valid$Xpert2Outcome_num ==0, 29]) #29 qXRv2, 33 Lunit
# skewness(Adult_Valid[Adult_Valid$Xpert2Outcome_num ==0, 33]) #33 Lunit

@@

###  Multi-ROC (Xpert Reference) 
```{r Multi-ROC_All_Xpert}
# make it long
Adult_Valid$qXRv2_100 <- Adult_Valid$qXRv2*100

Adult_Valid_long <- gather(Adult_Valid, DeepLearningSystem, AbnormalityScore, CAD4TB6, qXRv2_100)

############# Pooled ###############
roc_CAD6 <- ci.auc(Xpert2Outcome_num ~ CAD4TB6, Adult_Valid)
roc_qure <- ci.auc(Xpert2Outcome_num ~ qXRv2_100, Adult_Valid)
# roc_Lunit <- ci.auc(Xpert2Outcome_num ~ Lunit, Adult_Valid)
# Adult_Valid_long$DeepLearningSystem[Adult_Valid_long$DeepLearningSystem %in% "Lunit_100"] <- "Lunit"

Adult_Valid_long$DeepLearningSystem[Adult_Valid_long$DeepLearningSystem %in% "CAD4TB6"] <- "CAD4TB"
Adult_Valid_long$DeepLearningSystem[Adult_Valid_long$DeepLearningSystem %in% "qXRv2_100"] <- "qXR"

@@

for (i in 1:100){
myfunction <- function(CountryX, car.cutoff){
a <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="1")
b <- sum(CountryX$qXRv2 >= car.cutoff & CountryX$Xpert2Outcome_num =="0")
c <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="1")
d <- sum(CountryX$qXRv2 < car.cutoff & CountryX$Xpert2Outcome_num =="0")
dat <- as.table(matrix(c(a,b,c,d), nrow = 2, byrow = TRUE))
colnames(dat) <- c("Dis+","Dis-")
rownames(dat) <- c("Test+","Test-")
rval <- epi.tests(dat, conf.level = 0.95)
sensitivity <- as.vector(round((rval$elements$sensitivity),2)) 
specificity <- as.vector(round((rval$elements$specificity),2))
pv.positive <- as.vector(round((rval$elements$pv.positive),2))
pv.negative <- as.vector(round((rval$elements$pv.negative),2))
correct.rate <- round((a+d)/length(CountryX$Xpert2Outcome_num), 2)

perc_above_CAR_Score<- sum(CountryX$qXRv2 >= car.cutoff)/length(CountryX$TID_OMRS)
Score <- qure_ai_score[i]

>>>>

### Histogram 
```{r Histogram, fig.width=8, fig.height=5,}
# make it long
Adult_Valid$qXRv3_100 <- Adult_Valid$qXRv3*100

Adult_Valid_long <- gather(Adult_Valid, DeepLearningSystem, AbnormalityScore, CAD4TB6, qXRv3_100)

# p <- ggplot(Adult_Valid,aes(CAD4TB6))
# p <- ggplot(Adult_Valid,aes(qXRv3))
# p <- ggplot(Adult_Valid,aes(DrCADxScore))

@@

# library(moments)
# skewness(Adult_Valid[Adult_Valid$Xpert2Outcome_num ==1, 28]) #28 CAD4TB6, 29 qXRv3, 33 Lunit
# skewness(Adult_Valid[Adult_Valid$Xpert2Outcome_num ==1, 29]) #29 qXRv3, 33 Lunit
# skewness(Adult_Valid[Adult_Valid$Xpert2Outcome_num ==1, 33]) #33 Lunit
# 
# skewness(Adult_Valid[Adult_Valid$Xpert2Outcome_num ==0, 28]) #28 CAD4TB6, 29 qXRv3, 33 Lunit
# skewness(Adult_Valid[Adult_Valid$Xpert2Outcome_num ==0, 29]) #29 qXRv3, 33 Lunit
# skewness(Adult_Valid[Adult_Valid$Xpert2Outcome_num ==0, 33]) #33 Lunit

@@

###  Multi-ROC (Xpert Reference) 
```{r Multi-ROC_All_Xpert}
# make it long
Adult_Valid$qXRv3_100 <- Adult_Valid$qXRv3*100

Adult_Valid_long <- gather(Adult_Valid, DeepLearningSystem, AbnormalityScore, CAD4TB6, qXRv3_100)

############# Pooled ###############
roc_CAD6 <- ci.auc(Xpert2Outcome_num ~ CAD4TB6, Adult_Valid)
roc_qure <- ci.auc(Xpert2Outcome_num ~ qXRv3_100, Adult_Valid)
# roc_Lunit <- ci.auc(Xpert2Outcome_num ~ Lunit, Adult_Valid)
# Adult_Valid_long$DeepLearningSystem[Adult_Valid_long$DeepLearningSystem %in% "Lunit_100"] <- "Lunit"

Adult_Valid_long$DeepLearningSystem[Adult_Valid_long$DeepLearningSystem %in% "CAD4TB6"] <- "CAD4TB"
Adult_Valid_long$DeepLearningSystem[Adult_Valid_long$DeepLearningSystem %in% "qXRv3_100"] <- "qXR"

@@

for (i in 1:100){
myfunction <- function(CountryX, car.cutoff){
a <- sum(CountryX$qXRv3 >= car.cutoff & CountryX$Xpert2Outcome_num =="1")
b <- sum(CountryX$qXRv3 >= car.cutoff & CountryX$Xpert2Outcome_num =="0")
c <- sum(CountryX$qXRv3 < car.cutoff & CountryX$Xpert2Outcome_num =="1")
d <- sum(CountryX$qXRv3 < car.cutoff & CountryX$Xpert2Outcome_num =="0")
dat <- as.table(matrix(c(a,b,c,d), nrow = 2, byrow = TRUE))
colnames(dat) <- c("Dis+","Dis-")
rownames(dat) <- c("Test+","Test-")
rval <- epi.tests(dat, conf.level = 0.95)
sensitivity <- as.vector(round((rval$elements$sensitivity),2)) 
specificity <- as.vector(round((rval$elements$specificity),2))
pv.positive <- as.vector(round((rval$elements$pv.positive),2))
pv.negative <- as.vector(round((rval$elements$pv.negative),2))
correct.rate <- round((a+d)/length(CountryX$Xpert2Outcome_num), 2)

perc_above_CAR_Score<- sum(CountryX$qXRv3 >= car.cutoff)/length(CountryX$TID_OMRS)
Score <- qure_ai_score[i]

### 2020-07-28 SubGroup.Rmd
CAD6.3

  attr <- attributes(evalmod(scores = dataset$qXRv2, labels = dataset$Xpert2Outcome_num))
  aucT2 <- c("qXR ", round(attr$auc[4],3))

@@

aucTable <- rbind(all, New, Old, Young, Middle, Senior, Referral, DOTS, WalkIn, Female, Male)
colnames(aucTable) <- c("DL System", "AUC", "PCAUC", "Subgroup")
# write.csv(aucTable, "Results/aucTable.csv")
# rm(list=(ls()))
```

@@

library(pROC)
ROC <- function(dataset){
  roc_CAD6 <- ci.auc(Xpert2Outcome_num ~ CAD4TB6, dataset)
  roc_qure <- ci.auc(Xpert2Outcome_num ~ qXRv2_100, dataset)
  roc_Lunit <- ci.auc(Xpert2Outcome_num ~ LunitScore_100, dataset)
  roc_JF1 <- ci.auc(Xpert2Outcome_num ~ JF1_100, dataset)
  roc_IF2 <- ci.auc(Xpert2Outcome_num ~ IF2_100, dataset)

  aucT <- as.data.frame(matrix(c(roc_CAD6[2], roc_CAD6[1], roc_CAD6[3], roc_qure[2], roc_qure[1], roc_qure[3], roc_Lunit[2], roc_Lunit[1], roc_Lunit[3], roc_JF1[2], roc_JF1[1], roc_JF1[3], roc_IF2[2], roc_IF2[1], roc_IF2[3]),  byrow=TRUE, ncol =  3))
  names(aucT) <- c("AUC", "AUCL", "AUCH")
  aucT$DL.System <- c("CAD4TB", "qXR", "Lunit INSIGHT CXR", "JF CXR-1", "InferReadDR")

@@

aucTable$Subgroup <- factor(aucTable$Subgroup, levels = c("Young age", "Middle age", "Old age", "Referred", "DOTS retested", "WalkIn", "New cases", "Previously treated cases", "Female", "Male"))
### AUC
age<-ggplot(aucTable[aucTable$Subgroup %in% c("Young age", "Middle age", "Old age"), ], aes(x=DL.System, y=AUC, fill=Subgroup)) +  geom_bar(stat="identity", width=0.6, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))

referral<-ggplot(aucTable[aucTable$Subgroup %in% c("Referred", "DOTS retested", "WalkIn"), ], aes(x=DL.System, y=AUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))

history<-ggplot(aucTable[aucTable$Subgroup %in% c("New cases", "Previously treated cases"), ], aes(x=DL.System, y=AUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))

gender <- ggplot(aucTable[aucTable$Subgroup %in% c("Female", "Male"), ], aes(x=DL.System, y=AUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))

### PRC
agePC<-ggplot(aucTable[aucTable$Subgroup %in% c("Young age", "Middle age", "Old age"), ], aes(x=DL.System, y=PCAUC, fill=Subgroup)) +  geom_bar(stat="identity", width=0.6, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))

referralPC<-ggplot(aucTable[aucTable$Subgroup %in% c("Referred", "DOTS retested", "WalkIn"), ], aes(x=DL.System, y=PCAUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))

historyPC<-ggplot(aucTable[aucTable$Subgroup %in% c("New cases", "Previously treated cases"), ], aes(x=DL.System, y=PCAUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))

genderPC <- ggplot(aucTable[aucTable$Subgroup %in% c("Female", "Male"), ], aes(x=DL.System, y=PCAUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))

@@

tiff("Results/PRC AUC plot.tif", width = 9, height = 8, units = "in", res = 100)
grid.arrange(agePC, referralPC, historyPC, genderPC, ncol=2)
dev.off()

```{r}
ROCaucTable <- read.csv("Results/ROCaucTable.csv")
ROCaucTable$subgroup <- factor(ROCaucTable$subgroup, levels = c("Young age", "Middle age", "Old age", "Referred", "DOTS retested", "WalkIn", "New cases", "Previously treated cases"))
### AUC
age <-ggplot(ROCaucTable[ROCaucTable$subgroup %in% c("Young age", "Middle age", "Old age"), ], aes(x=DL.System, y=AUC, fill=subgroup)) +  geom_bar(stat="identity", width=0.6, position=position_dodge()) + geom_errorbar(aes(ymin=AUCL, ymax=AUCH), width=.2, position=position_dodge(0.7)) + theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05)) 
age

referral<-ggplot(ROCaucTable[ROCaucTable$subgroup %in% c("Referred", "DOTS retested", "WalkIn"), ], aes(x=DL.System, y=AUC, fill=subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05)) + geom_errorbar(aes(ymin=AUCL, ymax=AUCH), width=.2, position=position_dodge(0.6)) 
referral

history<-ggplot(ROCaucTable[ROCaucTable$subgroup %in% c("New cases", "Previously treated cases"), ], aes(x=DL.System, y=AUC, fill=subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05)) + geom_errorbar(aes(ymin=AUCL, ymax=AUCH), width=.2, position=position_dodge(0.6))

>>>>

  attr <- attributes(evalmod(scores = dataset$qXRv3, labels = dataset$Xpert2Outcome_num))
  aucT2 <- c("qXR ", round(attr$auc[4],3))

@@

aucTable <- rbind(all, New, Old, Young, Middle, Senior, Referral, DOTS, WalkIn, Female, Male)
colnames(aucTable) <- c("AI.Algorithm", "AUC", "PCAUC", "Subgroup")
write.csv(aucTable, "Results/aucTable.csv")
rm(list=(ls()))
```

```{r PRAUC CI}
data(P10N10)

s1 <- c(1, 2, 3, 4)
s2 <- c(5, 6, 7, 8)
s3 <- matrix(1:8, 4, 2)

# Join two score vectors
scores1 <- join_scores(s1, s2)

# Join two vectors and a matrix
scores2 <- join_scores(s1, s2, s3)

l1 <- c(1, 0, 1, 1)
l2 <- c(1, 0, 1, 1)
l3 <- c(1, 0, 1, 0)

# Join two label vectors
labels1 <- join_labels(l1, l2)
labels2 <- join_labels(l1, l3)

# A dataset with 20 samples for the good early retrieval performance level
samps3 <- create_sim_samples(20, 10, 10, "good_er")

# Calculate ROC and Precision-Recall curves
sscurves <- evalmod(scores = P10N10$scores, labels = P10N10$labels)

# Specify test dataset IDs names
smmdat1 <- mmdata(scores1, labels2, dsids = c(1,2))

# Use a sample dataset created by the create_sim_samples function
smmdat2 <- mmdata(samps3[["scores"]], samps3[["labels"]], dsids = samps3[["dsids"]])

# Calculate curves for multiple test datasets and keep all the curves
smcurves <- evalmod(smmdat2, raw_curves = TRUE)

autoplot(smcurves, "PRC", show_cb = TRUE)
```

@@

library(pROC)
ROC <- function(dataset){
  roc_CAD6 <- ci.auc(Xpert2Outcome_num ~ CAD4TB6, dataset)
  roc_qure <- ci.auc(Xpert2Outcome_num ~ qXRv3_100, dataset)
  roc_Lunit <- ci.auc(Xpert2Outcome_num ~ LunitScore_100, dataset)
  roc_JF1 <- ci.auc(Xpert2Outcome_num ~ JF1_100, dataset)
  roc_IF2 <- ci.auc(Xpert2Outcome_num ~ IF2_100, dataset)

  aucT <- as.data.frame(matrix(c(roc_CAD6[2], roc_CAD6[1], roc_CAD6[3], roc_qure[2], roc_qure[1], roc_qure[3], roc_Lunit[2], roc_Lunit[1], roc_Lunit[3], roc_JF1[2], roc_JF1[1], roc_JF1[3], roc_IF2[2], roc_IF2[1], roc_IF2[3]),  byrow=TRUE, ncol =  3))
  names(aucT) <- c("AUC", "AUCL", "AUCH")
  aucT$AI.Algorithm <- c("CAD4TB", "qXR", "Lunit INSIGHT CXR", "JF CXR-1", "InferReadDR")

@@

aucTable$Subgroup <- factor(aucTable$Subgroup, levels = c("Young age", "Middle age", "Old age", "Referred", "DOTS retested", "WalkIn", "New cases", "Previously treated cases", "Female", "Male"))
### AUC
age<-ggplot(aucTable[aucTable$Subgroup %in% c("Young age", "Middle age", "Old age"), ], aes(x=AI.Algorithm, y=AUC, fill=Subgroup)) +  geom_bar(stat="identity", width=0.6, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))

referral<-ggplot(aucTable[aucTable$Subgroup %in% c("Referred", "DOTS retested", "WalkIn"), ], aes(x=AI.Algorithm, y=AUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))

history<-ggplot(aucTable[aucTable$Subgroup %in% c("New cases", "Previously treated cases"), ], aes(x=AI.Algorithm, y=AUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))

gender <- ggplot(aucTable[aucTable$Subgroup %in% c("Female", "Male"), ], aes(x=AI.Algorithm, y=AUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))

### PRC
agePC<-ggplot(aucTable[aucTable$Subgroup %in% c("Young age", "Middle age", "Old age"), ], aes(x=AI.Algorithm, y=PCAUC, fill=Subgroup)) +  geom_bar(stat="identity", width=0.6, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))

referralPC<-ggplot(aucTable[aucTable$Subgroup %in% c("Referred", "DOTS retested", "WalkIn"), ], aes(x=AI.Algorithm, y=PCAUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))

historyPC<-ggplot(aucTable[aucTable$Subgroup %in% c("New cases", "Previously treated cases"), ], aes(x=AI.Algorithm, y=PCAUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))

genderPC <- ggplot(aucTable[aucTable$Subgroup %in% c("Female", "Male"), ], aes(x=AI.Algorithm, y=PCAUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))

@@

tiff("Results/PRC AUC plot.tif", width = 9, height = 8, units = "in", res = 100)
grid.arrange(agePC, referralPC, historyPC, genderPC, ncol=2)
dev.off()
```

```{r}
ROCaucTable <- read.csv("Results/ROCaucTable.csv")
ROCaucTable$subgroup <- factor(ROCaucTable$subgroup, levels = c("Young age", "Middle age", "Old age", "Referred", "DOTS retested", "WalkIn", "New cases", "Previously treated cases"))
### AUC
age <-ggplot(ROCaucTable[ROCaucTable$subgroup %in% c("Young age", "Middle age", "Old age"), ], aes(x=AI.Algorithm, y=AUC, fill=subgroup)) +  geom_bar(stat="identity", width=0.6, position=position_dodge()) + geom_errorbar(aes(ymin=AUCL, ymax=AUCH), width=.2, position=position_dodge(0.7)) + theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05)) 
age

referral<-ggplot(ROCaucTable[ROCaucTable$subgroup %in% c("Referred", "DOTS retested", "WalkIn"), ], aes(x=AI.Algorithm, y=AUC, fill=subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05)) + geom_errorbar(aes(ymin=AUCL, ymax=AUCH), width=.2, position=position_dodge(0.6)) 
referral

history<-ggplot(ROCaucTable[ROCaucTable$subgroup %in% c("New cases", "Previously treated cases"), ], aes(x=AI.Algorithm, y=AUC, fill=subgroup)) + geom_bar(stat="identity", width=0.5, position=position_dodge())+theme_minimal() + theme(legend.position = "top") +  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05)) + geom_errorbar(aes(ymin=AUCL, ymax=AUCH), width=.2, position=position_dodge(0.6))
